---
title: "Plot Line Graph"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{placeholder}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

The `demViz` package provides simple `ggplot2` wrapper functions for common graphs used in demography, public health and the social sciences.

One of the most common plots made when comparing estimates or data for different groupings (by location, sex, age, race, income etc.) is a line graph.

```{r ccmpp, echo = FALSE}
library(demViz)
library(ggplot2)
library(data.table)

# create population projections
thailand_population_estimates <- demCore::ccmpp(
  inputs = demCore::thailand_initial_estimates,
  settings = list(
    years = seq(1960, 1995, 5),
    sexes = c("female", "male"),
    ages = seq(0, 80, 5),
    ages_survival = seq(0, 85, 5),
    ages_asfr = seq(15, 45, 5)
  )
)
thailand_population_estimates[, source_name := "CCMPP Projection"]
thailand_population_estimates[, source_type := "Estimate"]

thailand_population_data <- copy(demCore::thailand_data$population)
thailand_population_data[, source_name := "Census Data"]
thailand_population_data[, source_type := "Data"]

# combine projections with population data
thailand_population <- rbind(
  thailand_population_estimates,
  thailand_population_data,
  use.names = T
)

# add 'age_name' column
hierarchyUtils::gen_name(thailand_population, col_stem = "age")
thailand_population[, age_name := factor(age_name, levels = unique(thailand_population[, age_name]))]

# add column differentiating the data to be plotted as a point
thailand_population[, point := source_type == "Data"]

```

To demonstrate `demViz::plot_line_graph` we'll use population projections and population data from the `demCore` package. This is what the plot input data looks like after some basic prep.

```{r show_input_data}
thailand_population
```

`plot_line_graph` requires that we specify what column in the input data corresponds to the x-value (`x_col`) and the y-value (`y_col`). The `point_col` argument specifies the data we want to plot as points rather than a line.

The `scale_manual` argument is a flexible argument that allows the user to specify manual values for different aesthetics like colour or linetype etc. Each aesthetic must have `col`, `legend_title` and `scale` attributes.

```{r plot_time_series, fig.width = 8, fig.height = 20}
plot_line_graph(
  dt = thailand_population,
  plot_title = "Thailand Population Time Series",
  x_col = "year",
  x_axis_title = "Year",
  y_col = "value",
  y_axis_title = "Population",
  y_axis_commas = TRUE,
  point_col = "point",
  scale_manual = list(
    colour = list(
      col = "source_name",
      legend_title = "Source",
      scale = c("Census Data" = "#A55B3B", "CCMPP Projection" = "#4DAF4A")
    )
  )
)
```
